Con

### 2024-12-16 Final/Regression_Final_12.11.Rmd
Squashed commit of the following:
commit 68f8653b09ea6801b0fbe145e60b4e10a5c68dfa
Author: mernaghp <bigbenshuffleboard@gmail.com>
Date:   Mon Dec 16 17:22:09 2024 -0500

    Paper minor edits

commit c97b16e7507fe799428ff684a2bc597bf43c5156
Author: mernaghp <bigbenshuffleboard@gmail.com>
Date:   Mon Dec 16 15:47:04 2024 -0500

    More paper revisions

commit ebd2ccd875820546915c30fee9b15df9ca2fabeb
Merge: 95fd5b2 1136e8b
Author: mernaghp <bigbenshuffleboard@gmail.com>
Date:   Mon Dec 16 13:41:09 2024 -0500

    Merge branch 'main' into pm

commit 95fd5b2f444f19850552e204951e69ab4fd56681
Autho

### Libraries
```{r}
library(dplyr)
library(glmnet)
library(car)
```

@@

### Cleansing
```{r}
data$Yrs_in_NHL <- 2016 - data$DftYr
data$A = data$A1 + data$A2

@@

scale_numeric <- function(x) x %>% mutate_if(is.numeric, function(y) as.vector(scale(y)))
scaled_data <- data %>% scale_numeric()
```

```{r}
bedrock <- lm(Salary_log ~ FO_pct + G + A + GF + GA + plus_mins + TOI + iSF + Yrs_in_NHL + Ht + Wt + Grit + iHF + iHA + iBLK + PIM + GP, data = scaled_data)
summary(bedrock)

e     <- resid(bedrock)
Yhat  <- predict(bedrock)
s     <- summary(bedrock)$sigma
es    <- e/s
```

@@

```{r}
vif(bedrock)
mean(vif(bedrock))
```
```{r, fig.width=10, fig.height=10}
pairwise <- subset(scaled_data, select = c(FO_pct, G, A, GF, GA, plus_mins, TOI, iSF, Yrs_in_NHL, Ht, Wt, Grit, iHF, iHA, iBLK, PIM, GP))

@@

### Penalized Regression
``` {r}
library(glmnet)
X         <- model.matrix(Salary_log ~ FO_pct + G + A + GF + GA + plus_mins + TOI + iSF + Yrs_in_NHL + Ht + Wt + Grit + iHF + iHA + iBLK + PIM + GP -1, data = scaled_data)
Y         <- scaled_data$Salary_log

@@

rownames(results) = c("Ridge", "Elastic", "Lasso-Like", "Lasso")
colnames(results) = c("Lambda", "MSE")
results
```
```{r}
plot(elastic_cv)
```

@@

```{r}
baseline <- lm(Salary_log ~ G + A + GF + plus_mins + TOI + iSF + Yrs_in_NHL + Wt + GP, data = scaled_data)
summary(baseline)

@@

```{r}
library(glmnet)
X         <- model.matrix(Salary_log ~ G + A + GF + plus_mins + TOI + iSF + Yrs_in_NHL + Wt + GP -1, data = scaled_data)
Y         <- scaled_data$Salary_log

ridge_cv   <- cv.glmnet(x = X, y = Y, family = "gaussian", alpha = 0, type.measure = "mse", nfolds = nrow(scaled_data), grouped = FALSE)

plot(ridge_cv)
```

```{r}
coef(ridge_cv)
```

>>>>

### Libraries
```{r}
library(dplyr)
library(glmnet)
library(car)
library(nestedcv)
```

@@

### Cleansing
```{r}
data$Yrs_in_NHL <- 2016 - data$DftYr
data$A = data$A1 + data$A2
data$Salary_log_corrected <- data$Salary_log

@@

scale_numeric <- function(x) x %>% mutate_if(is.numeric, function(y) as.vector(scale(y)))
scaled_data <- data %>% scale_numeric()

EDA = subset(scaled_data, select = c(Salary_log, G, A, plus_mins, TOI, iSF, Yrs_in_NHL, Ht, Wt, Grit, iHF, iHA, iBLK, GP))
```

```{r}
library(psych)
describe(data$Salary)
```
```{r}
hist(data$Salary)
```

```{r, fig.height=10}
plot(EDA[, 1:7])
```

```{r}
bedrock <- lm(Salary_log ~ FO_pct + G + A + GF + GA + plus_mins + TOI + iSF + Yrs_in_NHL + Ht + Wt + iHF + iHA + iBLK + Grit + GP, data = scaled_data)
summary(bedrock)
```
```{r}
vif(bedrock)
mean(vif(bedrock))
```

```{r, fig.height=10}
par(mfrow = c(2,2))
plot(bedrock)
```

### EDA
```{r, fig.height=7.5}
plot(scaled_data$TOI, scaled_data$Salary_log)
lines(lowess(scaled_data$TOI, scaled_data$Salary_log), col=2)
```

```{r}
scaled_data$A_2  <- scaled_data$A^2
scaled_data$TOI_2  <- scaled_data$TOI^2

scaled_data$iBLK_2  <- scaled_data$iBLK^2
scaled_data$Grit_2  <- scaled_data$Grit^2

bedrock_poly <- lm(Salary_log ~ G + A + GF + GA + plus_mins + TOI_2 + iSF + Yrs_in_NHL + Ht + Wt + iHF + iHA + iBLK + Grit + GP, data = scaled_data)

summary(bedrock_poly)
mean(vif(bedrock_poly))

```

```{r}
vif(bedrock_poly)
mean(vif(bedrock_poly))

```

```{r, fig.height = 10}
par(mfrow = c(2,2))
plot(bedrock_poly)
```

````{r}
confint(bedrock_poly, level = 0.95)
```

```{R}
library(xtable)
conf = confint(bedrock_poly, level = 0.99)

xtable(confint(bedrock_poly, level = 0.95))

```

@@

```{r, fig.width=10, fig.height=10}
pairwise <- subset(scaled_data, select = c(G, A, GF, GA, plus_mins, TOI, iSF, Yrs_in_NHL, Ht, Wt, iHF, iHA, iBLK, Grit, GP))

@@

### Penalized Regression
``` {r}
library(glmnet)
X         <- model.matrix(Salary_log ~ G + A + GF + GA + plus_mins + TOI + iSF + Yrs_in_NHL + Ht + Wt + iHF + iHA + iBLK + Grit + GP -1, data = scaled_data)
Y         <- scaled_data$Salary_log

@@

rownames(results) = c("Ridge", "Elastic", "Lasso-Like", "Lasso")
colnames(results) = c("Lambda", "MSE")
results
```
```{r}
plot(elastic_cv)
```
```{r}
summary(elastic_cv)
```

```{r}
coef(elastic_cv, s = "lambda.min")
```

@@

```{r}
baseline <- lm(Salary_log ~ A + GF + plus_mins + TOI + iSF + Yrs_in_NHL + Wt + GP, data = scaled_data)
summary(baseline)

@@

### Cross-Nested Validation
```{r}
library(glmnet)
library(nestedcv)
X         <- model.matrix(Salary_log ~ A + GF + plus_mins + TOI + iSF + Yrs_in_NHL + Wt + GP -1, data = scaled_data)
Y         <- scaled_data$Salary_log

test <- nestcv.glmnet(x = X, y = Y, family = "gaussian", alphaSet = seq(0, 0.3, 0.1), type.measure = "mse", n_outer_folds = 10, n_inner_folds = 10, grouped = FALSE)

plot(test$outer_result[[1]]$cvafit)

```
```{R}
summary(test)
```

### Penalized Regression

```{r}
library(psych)
describe(data$Salary)
```
```{r}
hist(data$Salary)
```

```{r, fig.height=10}
plot(EDA[, 1:7])
```
